Simultaneous Elicitation of Scoring Rule and Agent Preferences for Robust Winner Determination

### 2020-10-08 minimax.tex
related work

Focusing on positional scoring rules, we assume that the chair, while not able to give a precise definition of the rule, is capable of answering simple questions requiring to pick a winner from a specific example profile. In addition, the preferences of the agents are incrementally acquired by asking comparison queries. 
In this setting, we propose a method for robust approximate winner determination with minimax regret. We also provide an interactive elicitation protocol based on minimax regret and develop several query strategies that question the chair and the agents in order to acquire the most relevant information for quickly converging to a near-optimal alternative. Finally, we find out experimentally that questioning voters is more useful than questioning the chair in our setting.
\end{abstract}

@@

The traditional approach to social choice assumes that both the social choice function and the full preference orderings of the agents (voters) are expressed beforehand. These represent two strong hypothesis.
Requiring agents to express full preference orderings can be prohibitively costly (in terms of cognitive and communication cost).
This observation has motivated a number of recent works considering social choice with partial preference orders \citep{Xia2008, Pini2009, Konczak05} and incremental elicitation \citep{Kalech2011, Lu2011, Naamani-Dery2015,Benabbou2016} of agent preferences. \\ Furthermore, it is often difficult for non-expert users to formalize a voting rule on the basis of some generic preferences over a desired aggregation method. Thus, the first hypothesis should also be relaxed. 
%Also the first hypothesis should be relaxed considering that, in several situations, it may not be easy to precisely define the voting rule.Indeed, it is possible that the chair has some preferences over the desired aggregation method, but is not able to formalize the voting rule upfront.
When considering positional scoring rules, several authors \citep{Stein1994, Llamazares2013, Viappiani2018} have worked on positional scoring rules with uncertain weights, assuming that the preferences of the agents are fully known.
%it is possible to derive dominance relations (akin to stochastic dominance) that allow to eliminate some alternatives since they will be less preferred than another one for any instantiation of the weights \citep{Stein1994}.
%Among others, Llamazares and Pe{\~{n}}a have considered  the problem of dealing with underspecified weights in positional scoring rules.

@@

\paragraph{Experimental conclusions}
Our approach permits to compare experimentally strategies that question the chair, the voters, or both. We describe informally here a few of the conclusions stemming from these experiments, given a problem involving $m$ alternatives and $n$ agents. First, a good quality recommendation can be reached by asking what can be considered a reasonable number of questions to the chair and agents. For example, in a problem of size $m = 5$, $n = 10$, $55$ questions in total are required to reach a good quality recommendation, whcih can be considered reasonable as these questions are to be dispatched over $10$ agents and the chair.
Second, the quality of the recommendation increases faster than linearly with the number of questions, after only a few questions (the first few questions yield no increase in quality).
Third, we experimentally find out that asking questions to the agents only performs similarly than asking questions both to the agents and the chair, although questions to the chair do have a positive value in terms of quality of the recommendation.
%the value of information of one question to the chair is similar to the value of information of one question to a voter (in the ranges we considered), up to a certain proportion of questions asked to the chair. 
Knowing this permits to choose the questioning strategy wisely depending on the estimated cost of each kind of question, which depends on the application.

The paper is organized as follows. \Cref{sec:related} reviews the works related to our objective.
In Section \ref{sec:background} we provide the necessary background and in Section \ref{sec:mmr} we introduce the minimax criterion, that selects a winner that minimizes the worst possible regret.
Then, in Section \ref{sec:elicit} we provide an interactive elicitation protocol based on minimal regret;  in Section \ref{sec:experiments} we present the empirical validation of our approach with simulations; and Section \ref{sec:conclusions} provides some final thoughts.

\section{Related Work}
\label{sec:related}
%The work of \citet{Cailloux2014} provides elicitation methods for a quite general class of rules based on weak orders.
%it is possible to derive dominance relations (akin to stochastic dominance) that allow to eliminate some alternatives since they will be less preferred than another one for any instantiation of the weights \citep{Stein1994}.
%Among others, Llamazares and Pe{\~{n}}a have considered  the problem of dealing with underspecified weights in positional scoring rules.

@@

The max regret $\MaxR(x; \pprofile, W)$ is determined by considering the pairwise regret of $x$ with all other alternatives in $A$.
Optimal alternatives w.r.t. minimax regret are the ones with least max regret. 
Observe that, whenever the $\PMR$ of an alternative $x$ (against some other alternative $y$) exceeds the best MR value found so far, we do not need to further evaluate $x$. 
This idea can be exploited further by adopting a minimax-search tree \citep{Braziunas2011}.

@@

Let $(x^{*},\bar{y}, \bar{\profile}, \bar{\w})$ be the current solution of the minimax regret, where $\bar{y}, \bar{\profile}, \bar{\w}$ are, respectively, the choice of $y$, the completion of the profile and the selection of weights for which $x^{*}$ is the minimax optimal alternative. 
The \strat{Pessimistic} strategy considers a set of $n + m$ candidate questions: one per agent, and one per rank.
The candidate questions to the agents use the heuristic proposed by \citet{Lu2011}: for each agent $j$, if $x^*$ and $\bar{y}$ are incomparable in $\ppref_j$, the candidate question concerns the pair $(x^*, \bar{y})$, otherwise, the candidate question concerns the pair $(x^*, z)$ for some $z$ incomparable to $x^*$ (randomly chosen), or if none such $z$ exist, the pair $(\bar{y}, z)$ for some $z$ incomparable to $\bar{y}$, or, if both $x^*$ and $\bar{y}$ are comparable to every alternatives in $\ppref_j$, any incomparable pair is picked at random. 
To understand the intuition behind favoring these two alternatives for our questions, recall that, as shown in the proof of \cref{claim:completion}, in order to increase $\PMR(x^{*},\bar{y})$, an adversary should place as many alternatives as she can above $x^{*}$ if $x^* \ppref_j \bar{y}$, and between $\bar{y}$ and $x^{*}$ if $\bar{y} \ppref_j x^*$.  Asking questions involving $x^*$ or $\bar{y}$ thus has a particular chance of reducing usefully the possibilities of the adversary.
The candidate questions to the chair are determined as in the Random strategy.
The strategy then selects among these $n + m$ candidate questions one that leads to minimal regret in the worst case, considering both possible answers to the question. Assume that a question leads to the possible new knowledge states $(\pprofile_1, W_1)$ and $(\pprofile_2, W_2)$, depending on the answer, numbering them so that $\MMR(\pprofile_1, W_1) ≥ \MMR(\pprofile_2, W_2)$. Then the badness of the question in the worst case is:
\begin{align}
	\MMR(\pprofile_1,W_1) + \frac{1}{10000}\MMR(\pprofile_2, W_2).
\end{align}
This badness measure gives a way of picking questions among a set of possible questions, by picking one that minimizes this approximate measure of minimax regret {\em a posteriori}. 
We use this operator that is similar to a $\max$ operator because \citet{Cailloux2014} reported that pessimistic aggregation works much better than optimistic aggregation, although our experiments in this context suggested a weak impact of that choice on the performance of the strategy.
However, to avoid the absorption property of max, we adopt criterion closer to $\leximax$ as an aggregator: if the maximal $\MMR$ of two questions are (nearly) equal, then it considers the other $\MMR$ values, that are the one associated to the opposite answer, preferring the question with the lowest value.
(Technically, instead of applying a pure lexicographic aggregation, which is very sensitive to small errors due to floating-point computations, we apply a weighted sum between the maximal and the minimal $\MMR$ values, with a predominant weight to the maximal one.)

The \strat{Extended pessimistic} strategy uses the same criterion as the pessimistic strategy, but extending it to a bigger set of $m^2 n + m$ candidate questions, the same as those considered by the Random strategy.
After having selected the candidate questions, we apply the same operator as for the Pessimistic strategy: we evaluate, for each of the possible questions, the minimax regret for the two possible answers and we choose the best according to (quasi-)$\leximax$.
We use this strategy to test whether Pessimistic performs well: depending on the quality of the heuristic of the Pessimistic strategy, it might perform nearly equally well, or perhaps even better, than Extended pessimistic, while being (much) more efficient. We expect that Extended pessimistic will be applicable only to very small problem instances: its complexity is in $O(n^2 m^5)$, because we consider $O(m^2)$ questions for each agent and need for each question to compute $\MMR$ twice, whose complexity is $O(nm^3)$.

The \strat{Two phases} strategy is developed in order to investigate the effect of varying the proportion of questions asked to agents and to the chair, and compare the performance of asking questions to the chair first or to the voters first. 
The \strat{Two phases - ac} variant first asks $p$ questions to the agents, then $k-p$ questions to the chair, using in both cases Pessimistic to select the specific questions; whereas the \strat{Two phases - ca} variant starts with $p$ questions to the chair, then questions the agents. 
%Note that when asking first only questions to the chair, if the obtained knowledge approximates well the scoring vector, then in the second part of the elicitation we fall into the more classical setting of incompleteness of preferences assuming a known voting rule. 
%And vice-versa when asking first questions to the agents, the second part of the elicitation is similar to the setting of incompletely specified scoring rule. 
%This strategy also permits to simulate the current state of the art when considering incomplete preferences. By asking enough questions to the chair we can reduce our problem into a well studied one of incompleteness of preferences knowing the voting rule. Similarly, if we invert to whom ask questions first, we fall instead in an already studied case of uncertainty of the voting rule with a known complete profile.

@@

\section{Empirical Evaluation} 
\label{sec:experiments}
\commentOC{
	\begin{enumerate}
		\item Pessimistic VS Elitist
		\item Reach regret: $n/10$. For this, we need $m^x n$ questions. 
		\item Value of information qC VS qV with 2 phases and 2phases VS interleaving
		\begin{itemize}
			\item Interleaving $k$ questions is similar to asking $p$ questions to the chair first and then $k - p$ to the voters when $p$ is chosen optimally. [do this a bit later]
			\item A question to the chair has a similar value (in regret) as a qV: use the graph summarized by Olivier. Check prop. qC. Check on other sizes.
		\end{itemize}
		\item find a way of displaying the graph so that it is understandable in B/W.
		\item Time comparison XPess VS Pess?
		\item Check Pess VS XPess on other sizes.
		\item ?
	\end{enumerate}
}
Our experiments are described by topic here below. We generally use the following protocol, deviations are indicated below for each experiment.

@@

\subsection{Judging Pessimistic relatively}
\begin{table}
	\begin{center}
		\resizebox{\columnwidth}{!}{
		\begin{tabular}{S[table-figures-integer=3, table-number-alignment = right, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]}
			\toprule
			{k} & {Rnd.} & {sd} & {Pes.} & {sd} & {Ex.\ pes.} & {sd} & {Eli.} & {sd} \\
			\midrule
			0 & 10.0 & 0.0 & 10.0 & 0.0 & 10.0 & 0.0 & 10.0 & 0.0\\
			20 & 9.06 & 0.49 & 5.85 & 0.87 & 6.17 & 0.78 & 6.32 & 0.61\\
			40 & 7.35 & 0.82 & 2.57 & 1.05 & 2.98 & 0.99 & 3.37 & 0.83\\
			60 & 5.74 & 1.03 & 0.67 & 0.67 & 0.77 &0.78 & 2.33 & 1.05\\
			80 & 4.10 & 1.15 & 0.03 & 0.12 & 0.05 & 0.18 & 2.28 & 1.05\\
			100 & 2.63 & 1.19 & 0.0 &  0.0 & 0.0 & 0.0& 2.28 & 1.05\\
			\bottomrule
		\end{tabular}
		}
	\end{center}
	\caption{Average MMR in problems of size $(5, 10)$ after $k$ questions and $200$ runs.}
	\label{tab:smallSize}
\end{table}

\begin{figure}
	\centering
	\includegraphics[width=.45\textwidth]{comparison.png}
	\caption{Plot in support of \cref{tab:smallSize}}
	\label{fig:smallSize}
\end{figure}

Our first experimental result concerns small size situations. We picked $m = 5, n = 10$ to illustrate our results (variations around this size yield similar conclusions). 
\Cref{tab:smallSize} and \cref{fig:smallSize} compares some of our strategies in this case.
We see that that Pessimistic performs better than Random and Extended pessimistic on a small size problem.
(These figures also display the performance of the Elitist strategy, to which we will come back.)

We observe that the Pessimistic strategy is able to reduce the regret almost completely after $30$ questions. We also see that Pessimistic performs slightly better than Extended pessimistic, showing that Pessimistic chooses candidate questions wisely; this is good news since (for $m = 5$ and $n = 10$), the latter strategy is much faster and takes only $15s$ for a complete elicitation session, while the former takes $80s$.

Asking Random questions does not permit to reach a low regret level even after having asked 100 questions, whereas a low regret level (MMR = 1) is reached by Pessimistic before having asked 60 questions.

We also see that Extended pessimistic performs slightly less well than Pessimistic. Although they come close, Extended pessimistic performs significatively less well, in the sense that the numbers are consistently in favor of Pessimistic if running the experiment again.

We next focus on the Pessimistic strategy, because Extended pessimistic is too slow to be ran repeatedly on much bigger problem sizes.

\subsection{Judging Pessimistic absolutely}
\label{sec:lowRegret}
\begin{table}
	\begin{center}
		\begin{tabular}{S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]S[table-number-alignment = center]S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]}
			\toprule
			{m} & {n} & {$\frac{n}{10}$} & {$k_{\MMR}$} & {$0.4 m^{1.6} n$} \\
			\midrule
			5 & 10 & 1.0 & 60 &  55 \\
			5 & 15 & 1.5 & 80 &  83 \\
			5 & 20 & 2.0 & 110 &  110 \\
			10 & 20 & 2.0 & 340 &  341 \\
			10 & 30 & 3.0 & 527 &  512 \\
			15 & 30 & 3.0 &  &  991 \\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Number of questions needed by Pessimistic strategy to reach $\MMR=\frac{n}{10}$ (represented by $k_{\MMR}$), for various problem sizes.}
	\label{tab:lowRegret}
\end{table}

The previous section compares Pessimistic to other strategies. In this set of experiments, we wonder about the absolute quality of Pessimistic. For practical usability, it is important to know how many questions should be asked in order to reach a low regret level. Here, we consider a low level to be a tenth of the number of voters ($n/10$): such a regret is equivalent to the difference of score of an alternative $x$ that results from switching from a profile $P$ to a profile $P'$ where ten percent of the voters rank $x$ last instead of first.
The results for various sizes are displayed in \cref{tab:lowRegret}. From these numbers, we obtain the function $0.4m^{1.6}n$ as a general approximation formula for the number of questions required to reach a low regret level. We see that the number of questions required grows approximately linearly with the number of voters and grows less fast than the square of the number of alternatives, for the sizes we considered. In other words, on average, assuming no questions get asked to the committee, each voter will have to answer $0.4m^{1.6}$ questions in order to to reach a low regret level. For $m = 5$, that is about $6$ questions per voter; for $m = 10$, that is about $17$ questions per voter; and for $m = 15$, that is about $33$ questions per voter.

\subsection{Comparing with full elicitation}
In this work, we advocate obtaining an approximate winner without obtaining the full profile or determine completely the voting rule. The previous section evaluate the number of questions per voter to reach a low regret value.
In this section we want to contrast our approach to one that would obtain the full profile on the one hand, and determine the voting rule on the other hand. More precisely, we want to estimate the number of questions that would be required to elicit the complete profile. We focus on the profile because eliciting the scores to full precision would require infinitely many questions, with the questions we use. 
Note that this may underestimate the number of questions required to determine completely the profile and the rule, as questions to the agents yield no information about the scoring vector.

To estimate this number, we draw one linear order randomly (with equiprobability over all possible linear orders) and assume the following querying process: given a partial ordering representing our knowledge so far of an agent preferences, we pick a question equiprobably among the remaining edges, and add the edge in the appropriate direction to our partial ordering. We count the average number of questions required to reach a complete ordering.

\subsection{Decrease in MMR values}
\begin{figure}
	\centering
	\includegraphics[width=.45\textwidth]{linearity.png}
	\caption{Average $\MMR$ after $k$ questions with Pessimistic strategy after 10 runs for different problem sizes.}
	\label{fig:linearity}
\end{figure}

We next wonder how fast the regret decreases, measured as a function of the number of questions asked. This is important practically because it may be impossible or unwanted to ask enough questions to reach low level of regrets, as computed in \cref{sec:lowRegret}. Knowing the speed of decrease thus permits to know which trade-offs can be achieved between the quality of the resulting recommendation and the number of questions that participants have to answer. \Cref{fig:linearity} shows graphically the decrease in $\MMR$ according to the number of questions asked for various problem sizes. We see that this function is convex, apart from the very few questions, indicating to users of our approach that asking, for example, half the number of questions required to reach a low regret value will still yield a significant gain in regret, namely, more than half the distance to the low regret value.

>>>>

Focusing on positional scoring rules, we assume that the chair, while not able to give a precise definition of the rule, is capable of answering simple questions requiring to pick a winner from a specific example profile. In addition, the preferences of the agents are incrementally acquired by asking comparison queries. 
In this setting, we propose a method for robust approximate winner determination with minimax regret. We also provide an interactive elicitation protocol based on minimax regret and develop several query strategies that question the chair and the agents in order to acquire the most relevant information for quickly converging to a near-optimal alternative.
\end{abstract}

@@

The traditional approach to social choice assumes that both the social choice function and the full preference orderings of the agents (voters) are expressed beforehand. These represent two strong hypothesis.
Requiring agents to express full preference orderings can be prohibitively costly (in terms of cognitive and communication cost).
This observation has motivated a number of recent works considering social choice with partial preference orders \citep{Xia2008, Pini2009, Konczak05} and incremental elicitation \citep{Kalech2011, Lu2011, Naamani-Dery2015,Benabbou2016} of agent preferences. \\ Furthermore, it is often difficult for non-expert users to formalize a voting rule on the basis of some generic preferences over a desired aggregation method. Thus, the first hypothesis should also be relaxed. 
%Also the first hypothesis should be relaxed considering that, in several situations, it may not be easy to precisely define the voting rule.Indeed, it is possible that the chair has some preferences over the desired aggregation method, but is not able to formalize the voting rule upfront.

%it is possible to derive dominance relations (akin to stochastic dominance) that allow to eliminate some alternatives since they will be less preferred than another one for any instantiation of the weights \citep{Stein1994}.
%Among others, Llamazares and Pe{\~{n}}a have considered  the problem of dealing with underspecified weights in positional scoring rules.

@@

\paragraph{Experimental conclusions}
Our approach permits to compare experimentally strategies that question the chair, the voters, or both. We describe informally here a few of the conclusions stemming from these experiments, given a problem involving $m$ alternatives and $n$ voters. First, low levels of regret can be reached by asking approximately $m n$ questions to the voters and $m$ questions to the chair. 
Second, the decrease in $\MMR$ is approximately linear with the number of questions asked, except when the regret approaches zero. \commentBN{Not true anymore, some example with Pess (former Lim.Pes.) 
$\begin{array}{ccc}
	k \quad & \textbf{(5,10)}&\textbf{(10,20)}\\
	0 \quad &10&20\\
	10 \quad &7.93&19.5\\
	20 \quad &5.85&18.2\\
	30 \quad &4.31&17.43\\
	40 \quad &3.01&16.56\\
	50 \quad &1.95&15.59\\
	100 \quad &0.0&11.91\\
	150 \quad &0.0&8.92\\
	200 \quad &0.0&6.24\\
\end{array}
$
}\\
Third, the value of information of one question to the chair is similar to the value of information of one question to a voter (in the ranges we considered). Knowing this permits to choose the questioning strategy wisely depending on the estimated cost of each kind of question, which depends on the application.

The paper is organized as follows.
In Section \ref{sec:background} we provide the necessary background and in Section \ref{sec:mmr} we introduce the minimax criterion, that selects a winner that minimizes the worst possible regret.
Then, in Section \ref{sec:elicit} we provide an interactive elicitation protocol based on minimal regret;  in Section \ref{sec:experiments} we present the empirical validation of our approach with simulations; and Section \ref{sec:conclusions} provides some final thoughts.

\section{Related Work}
The recent growing interest in voting theory has also led to an increase in attention to its problems. One of these, the full information assumption; which has driven an increasing number of authors to question its validity. \citet{Conitzer2005} have studied the complexity of communication, using different voting rules, determining lower and upper bounds for it. They showed that, in the worst case, the agents should send their complete set of preference for most of the rule investigated. Considering then, cases where the information of agent preferences is only partial, \citet{Konczak05} have proposed a way to compute possible and necessary winners. They also showed that, even though this computation is hard in the general case, their method is polynomial in case of positional scoring rule. Later on, for the necessary winner problem, other authors have proposed polynomial-time algorithms when using maximin and Bucklin \citep{Xia2008}; sufficient conditions that assure tractability have been proved \citep{Pini2007}; and the uncertainty in weights has been considered \citep{Walsh2007,Viappiani2018}.
From this starting point several studies on elicitation of agent preferences have been proposed \citep{Naamani-Dery2015,Kalech2011,Lu2011,Pini2009,Benabbou2016,Cailloux2014,Dey2016,Dey2016_2}, and analysis on when to stop the elicitation process have been conducted \citep{Walsh2009,Conitzer2009}. Although more interest

Although more interest has been shown in the incompleteness of agent preferences, several authors have considered scenarios where the voting rule is partially defined.  \citep{Stein1994, Viappiani2018}. Among others, \citet{Llamazares2013} have considered  the problem of dealing with variable weights in positional scoring rules.

In this context, questions on the manipulability of voting rules have begun to arise. In fact, studies on the reactions of agents after others actions have been proposed \citep{Endriss2016,Dey2018,Dey2018_2}. It is worth precising that, in our work, we consider the agents to give their preferences in a secret way.

@@

The max regret $\MaxR(x; \pprofile, W)$ is determined by considering the pairwise regret of $x$ with all other alternatives in $A$.
Optimal alternatives w.r.t. minimax regret are the ones with least max regret. 
Observe that, whenever the $\PMR$ of an alternative $x$ (against some other alternative $y$) exceeds the best MR value found so far, we don't need to further evaluate $x$. 
This idea can be exploited further by adopting a minimax-search tree \citep{Braziunas2011}.

@@

The \strat{Pessimistic} strategy considers the same candidate questions as the Random strategy, but instead of picking one among those randomly, selects the question that leads to minimal regret in the worst case, considering both possible answers to the question. Assume that a question leads to the possible new knowledge states $(\pprofile_1, W_1)$ and $(\pprofile_2, W_2)$, depending on the answer. Then the badness of the question in the worst case is:
\begin{align}
	\max_{i=1,2} \MMR(\pprofile_i,W_i)
\end{align}
This badness measure gives a way of picking questions among a set of possible questions, by picking one that minimizes ths measure of minimax regret {\em a posteriori}. 
Note that other aggregators than $\max$ can be used as well. 
We use the $\max$ operator because \citet{Cailloux2014} reported that pessimistic aggregation works much better than optimistic aggregation, although our experiments in this context suggested a weak impact of that choice on the performance of the strategy.
However, to avoid the absorption property of max, we adopt the $\leximax$ criterion as an aggregator: if the maximal $\MMR$ of two questions are equal, then it considers the other $\MMR$ values, that are the one associated to the opposite answer, preferring the question with the lowest value.
(Technically, instead of applying a pure lexicographic aggregation, which is very sensitive to small errors due to floating-point computations, we apply a weighted sum between the maximal and the minimal $\MMR$ values, with a predominant weight to the maximal one.)
We expect this strategy to perform very well, but only for very small problem instances: its complexity is in $O(n^2 m^5)$, because we consider $O(m^2)$ questions for each agent and need for each question to compute $\MMR$ twice, whose complexity is $O(nm^3)$. For small dimensions, it estimates an upper bound to the possible quality of a myopic strategy.

The \strat{Limited pessimistic} strategy uses the same criterion as the pessimistic strategy, but limiting it to a small set of $n + m$ candidate questions: one per agent, and one per rank. Let $(x^{*},\bar{y}, \bar{\profile}, \bar{\w})$ be the current solution of the minimax regret, where $\bar{y}, \bar{\profile}, \bar{\w}$ are, respectively, the choice of $y$, the completion of the profile and the selection of weights for which $x^{*}$ is the minimax optimal alternative. 
The \strat{Limited pessimistic} strategy first selects $n$ candidates questions to the agents using the heuristic proposed by \citet{Lu2011}: for each agent $j$, if $x^*$ and $\bar{y}$ are incomparable in $\ppref_j$, the candidate question concerns the pair $(x^*, \bar{y})$, otherwise, the candidate question concerns the pair $(x^*, z)$ for some $z$ incomparable to $x^*$ (randomly chosen), or if none such $z$ exist, the pair $(\bar{y}, z)$ for some $z$ incomparable to $\bar{y}$, or, if both $x^*$ and $\bar{y}$ are comparable to every alternatives in $\ppref_j$, any incomparable pair is picked at random. 
To understand the intuition behind favoring these two alternatives for our questions, recall that, as shown in the proof of \cref{claim:completion}, in order to increase $\PMR(x^{*},\bar{y})$, an adversary should place as many alternatives as she can above $x^{*}$ if $x^* \ppref_j \bar{y}$, and between $\bar{y}$ and $x^{*}$ if $\bar{y} \ppref_j x^*$. 
\commentOC{I do not understand the reasoning in the next sentence.}
An intuitive way to reduce the pairwise max regret would be, therefore, to ask questions involving such alternatives, hoping for an answer that would prevent the adversary to play his best game. 
The candidate questions to the chair are determined as in the Random and Pessimistic strategies.
After having selected the candidate questions, we apply the Pessimistic strategy: we evaluate, for each of the questions, the minimax regret for the two possible answers and we choose the best according to $\leximax$.

The \strat{Two phases} strategy is developed in order to investigate the effect of varying the proportion of questions asked to agents and to the chair, and compare the performance of asking questions to the chair first or to the voters first. 
The \strat{Two phases - ac} variant first asks $p$ questions to the agents, then $k-p$ questions to the chair, using in both cases Limited pessimistic to select the specific questions; whereas the \strat{Two phases - ca} variant starts with $p$ questions to the chair, then questions the agents. 
%Note that when asking first only questions to the chair, if the obtained knowledge approximates well the scoring vector, then in the second part of the elicitation we fall into the more classical setting of incompleteness of preferences assuming a known voting rule. 
%And vice-versa when asking first questions to the agents, the second part of the elicitation is similar to the setting of incompletely specified scoring rule. 
This strategy also permits to simulate the current state of the art when considering incomplete preferences. By asking enough questions to the chair we can reduce our problem into a well studied one of incompleteness of preferences knowing the voting rule. Similarly, if we invert to whom ask questions first, we fall instead in an already studied case of uncertainty of the voting rule with a known complete profile.

@@

\section{Empirical Evaluation} 
\label{sec:experiments}
\commentOC{
	\begin{enumerate}
		\item Pessimistic is feasible and much better than Random
		\begin{itemize}
			\item Graph featuring (5, 10, 150, 200 runs), Random, Pess, L. pess, Elitist.
			\item And table like table 1.
		\end{itemize}
		\item Limited pessimistic performs well.
		\begin{itemize}
			\item Reach regret: $n/10$. For this, we need $m^x n$ questions. TODO Olivier: find $x$. TODO Beatrice: check and compile results in a table specifically for this (see: function regret by k).
			\item Almost as good as Pess and better than the Elitist one (see previous graphs or table)
			\item Much faster [do this much later]
		\end{itemize}
		\item Decrease in MMR is linear with nb of questions
		\begin{itemize}
			\item Redo nice graph of Beatrice with same sizes.
		\end{itemize}
		\item Value of information qC VS qV with 2 phases and 2phases VS interleaving
		\begin{itemize}
			\item Interleaving $k$ questions is similar to asking $p$ questions to the chair first and then $k - p$ to the voters when $p$ is chosen optimally. [do this a bit later]
			\item A question to the chair has a similar value (in regret) as a qV: use the graph summarized by Olivier. Check prop. qC. Check on other sizes.
		\end{itemize}
		\item Limited pessimistic approx Limited optimistic [do this much later]
	\end{enumerate}
}
Our experiments are described by topic here below. We generally use the following protocol, deviations are indicated below for each experiment.

@@

\subsection{Small size elections}
Our first experimental result concerns small size situations. We picked $m = 5, n = 10$ to illustrate our results (variations around these sizes yield similar conclusions). In such situations, we can run the resource-consuming Pessimistic strategy. Table x / graph x compares it to other strategies. We see that these strategies perform much better than random, even when its parameter $\pi$ is chosen in an optimal way, that is, when the proportion of questions asked to the chair is ideal. We also see a first important positive result for applicability of our approach, namely, that it is possible to reach a small regret with a reasonable number of questions in such problems.

\subsection{Limited pessimistic}
We next investigate the better performing Limited pessimistic strategy, because Pessimistic is too slow to be ran repeatedly on much bigger problem sizes.

\subsection{Our previous presentation}
\sisetup{round-mode=places, round-precision=2, table-figures-integer=2, table-figures-decimal=2}
\begin{table}
	\begin{center}
		\resizebox{\columnwidth}{!}{
		\begin{tabular}{S[table-figures-integer=3, table-number-alignment = right, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]}
			\toprule
			{k} & {Rnd.} & {sd} & {Pes.} & {sd} & {Ex.\ pes.} & {sd} & {Eli.} & {sd} \\
			\midrule
			0 & 10.0 & 0.0 & 10.0 & 0.0 & 10.0 & 0.0 & 10.0 & 0.0\\
			20 & 9.06 & 0.49 & 5.85 & 0.87 & 6.17 & 0.78 & 6.32 & 0.61\\
			40 & 7.35 & 0.82 & 2.57 & 1.05 & 2.98 & 0.99 & 3.37 & 0.83\\
			60 & 5.74 & 1.03 & 0.67 & 0.67 & 0.77 &0.78 & 2.33 & 1.05\\
			80 & 4.10 & 1.15 & 0.03 & 0.12 & 0.05 & 0.18 & 2.28 & 1.05\\
			100 & 2.63 & 1.19 & 0.0 &  0.0 & 0.0 & 0.0& 2.28 & 1.05\\
			\bottomrule
		\end{tabular}
		}
	\end{center}
	\caption{Average $\MMR$ in problems of size $(5, 10)$ after $k$ questions and $200$ runs.\commentBN{Attention, I already corrected the table with the new names. The column Pes. here is the Limited Pessimistic, I inverted them to follow the presentation order.}}
	\label{tab:comparison}
\end{table}

\begin{figure}
	\centering
	\includegraphics[width=.45\textwidth]{comparison.png}
	\caption{Plot in support of \cref{tab:comparison}}
	\label{fig:comparison}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=.45\textwidth]{linearity.png}
	\caption{Average $\MMR$ after $k$ questions with Pessimistic strategy after 10 runs for different problem sizes.}
	\label{fig:linearity}
\end{figure}

\begin{table}
	\begin{center}
		\begin{tabular}{S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]S[table-number-alignment = center]S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]}
			\toprule
			{m} & {n} & {$\frac{n}{10}$} & {$k_{\MMR}$} & {$m\cdot n +m^?$} \\
			\midrule
			5 & 10 & 1.0 & 60 &  \\
			5 & 15 & 1.5 & 80 &  \\
			5 & 20 & 2.0 & 110 &  \\
			10 & 20 & 2.0 & 340 &  \\
			10 & 30 & 3.0 & 527 &  \\
			15 & 30 & 3.0 & 919 &  \\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Number of questions needed by Pessimistic strategy to reach $\MMR=\frac{n}{10}$ (represented by $k_{\MMR}$), for different problem sizes.}
	\label{tab:linearity}
\end{table}

We test our strategies using randomly generated datasets. 
Our first goal is to see, with a small problem size ($m = 5, n = 5$) and the (time consuming) Pessimistic strategy, if an important lowering of the maximal regret can be achieved with a reasonable number of questions. We also want to estimate how “hard” such a problem is, by using the Random strategy as a baseline. Third, we want to estimate the loss (in terms of worst regret) when switching to the faster Limited pessimistic strategy. Fourth, we want to see, on a bigger problem size ($m = 10, n = 20$), how many questions must be asked for that strategy to achieve a significant reduction of the worst regret. Finally, we want to evaluate, thanks to the Two phases strategy, the impact of varying the proportion of questions asked to the agents (with respect to questions asked to the chair) on the reduction of the worst regret.
%We also want to see how realistic our approach is for various problem sizes, by estimating the number of questions we would have to ask before being able to reduce the worst regret significantly.

The results are displayed in \cref{tab:comparison,fig:linearity,tab:twoP}, where strategies are designated by Rnd for Random, Pes. for Pessimistic, L.\ pes. for Limited pessimistic and 2 ph. for Two phases.

We observe that the Pessimistic strategy is able to reduce the regret almost completely after $30$ questions. We also see that Limited pessimistic performs almost as well as Pessimistic; this is good news since (for $m=5$ and $n=5$), the former strategy is much faster and takes only $2.6s$ for a complete elicitation session, while the latter takes $16s$.
%However, it takes $1000$ times more time than the \strat{Random} strategy ($16s$ of the Pessimistic compared to $0.014s$ of the Random). Moreover, the results of the \strat{Limited pessimistic}, that takes almost $80\%$ less of the time of the \strat{Pessimistic} ($2.6s$), are essentially the same.
%In Table \ref{fig:1020}, we can see the drop of regret using a bigger instance.
%Finally in Table \ref{fig:p}
%
%\begin{table}
%	\begin{center}
%		\begin{tabular}{S[table-figures-integer=3, table-number-alignment = right, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]}
%			\toprule
%			{p} & {Comm. Fst.} & {sd} & {Vot. Fst.} & {sd} \\
%			\midrule
%			0 & 0.48 &0.59 & 0.48 &0.59  \\
%			50 & 0.01 & 0.04& 0.0 & 0.0 \\
%			100 & 0.04 & 0.09 & 0.13 & 0.35 \\
%			150 & 0.68 & 0.65 & 0.66 & 0.77 \\
%			200 &   &  &  &  \\
%			250 & 3.2 & 1.67 & 4.07	& 1.51 \\
%			300 &&&& \\
%			350 &&&& \\
%			400 &&&& \\
%			450 &&&& \\
%			500 &&&& \\
%			\bottomrule
%		\end{tabular}
%	\end{center}
%	\caption{Average regret in problems of size $(10, 20)$ after $500$ questions and $10$ runs. Where $p$ represents the number of questions asked to the chair.}
%	\label{tab:twoP500}
%\end{table}
